Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-01-31 appendix/appendixA.Rmd
Figure numbers, sp

```{r optional_plotting_config, include=FALSE}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

## Unlike classic Graham-Schaefer, this assumes harvest 
## occurs right after assessment, before recruitment
f <- function(x, h){ 
    s <- pmax(x-h, 0) 
    s + s * r * (1 - s / K) 
}
```

@@

```{r fig.width=5, fig.height=5}
det_sims %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line(lwd=1) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

```{r eval=FALSE}
dir.create(log_dir)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

```{r pomdp_sims}
set.seed(12345)

unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario")
```

@@

```{r}
sims <- bind_rows(static_sims, pomdp_sims) %>%
    left_join(meta) %>%  ## include scenario information (sigmas; etc)
    mutate(state = states[state], action = actions[action]) %>%
    select(time, state, rep, method, sigma_m, sigma_g, value)

@@

```{r}
sims <- read_csv(file.path(log_dir, "sims.csv"), col_types = "inicnnn")

@@

```{r}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g %in% c("0.1", "0.15")) %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
```

@@

```{r}
overest <-
bind_rows(static_sims, pomdp_overest_sims) %>%
  left_join(meta, by = "scenario") %>%  ## include scenario information (sigmas; etc)
  mutate(state = states[state], action = actions[action]) %>%
  select(time, state, rep, method, sigma_m, sigma_g, value) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  filter(sigma_g == "0.15") %>% 
  ungroup()

@@

```{r}
read_csv(file.path(log_dir, "overest_sims.csv")) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))
```

@@

```{r}
bind_rows(policy_table,
  data_frame(state = states, 
             policy = "SDP",
             harvest = actions[mdp$policy],
             escapement = states - actions[mdp$policy])) %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8)) + 
  labs(caption = "SDP solution when sigma_g = 0.1")
```

@@

```{r}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0) %>%
  pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount)

@@

```{r}
p1 <- recode_policies %>%
  ggplot(aes(state, escapement, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.8))

p1
```

```{r}
p2 <- recode_policies %>%
  ggplot(aes(state, harvest, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.6))

p2
```

@@

```{r}
p3 <- read_csv(file.path(log_dir, "priors.csv")) %>%
ggplot(aes(state, prior, col = policy)) + 
  geom_line(lwd=1) +
  coord_cartesian(xlim = c(0,1))
p3
```

@@

```{r}
sim$df %>%
  select(-value) %>%
  mutate(state = states[state], action = actions[action], obs = observations[obs]) %>%
  gather(variable, stock, -time) %>%
  ggplot(aes(time, stock, color = variable)) + 
  geom_line(lwd=1)  + scale_color_manual(values = unname(colors))
```

@@

```{r}
sim$state_posterior %>% 
  data.frame(time = 1:Tmax) %>%
  filter(time %in% seq(1,Tmax, by = 3)) %>%
  gather(state, probability, -time, factor_key =TRUE) %>% 
  mutate(state = states[as.numeric(state)]) %>% 
  ggplot(aes(state, probability, group = time, alpha = time)) + 
  geom_line(lwd = 1) + 
  coord_cartesian(xlim = c(0,1.5))

>>>>

```{r optional_plotting_config, cache = FALSE, include=FALSE}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

@@

## Unlike classic Gordon-Schaefer, this assumes harvest 
## occurs right after assessment, before recruitment
f <- function(x, h){ 
    s <- pmax(x-h, 0) 
    s + s * r * (1 - s / K) 
}
```

@@

```{r S1, fig.width=5, fig.height=5,fig.cap = "MSY, TAC, and CE policies under deterministic simulation. MSY and CE converge to the same standing biomass long term, but CE reaches this level more quickly.  TAC always harvests less than MSY, resulting in a higher standing biomass but lower long-term yeild. Note that POMDP is identical to CE when no uncertainty is present."}
det_sims %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line(lwd=1) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

```{r eval=!file.exists(file.path(log_dir, "meta.csv"))}
dir.create(log_dir)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

```{r pomdp_sims, eval=!file.exists(file.path(log_dir, "pomdp_sims.csv"))}
set.seed(12345)

unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario")

write_csv(pomdp_sims, file.path(log_dir, "pomdp_sims.csv"))
```

@@

```{r}
pomdp_sims <- read_csv(file.path(log_dir, "pomdp_sims.csv")) %>% 
  mutate(scenario = as.character(scenario))

sims <- bind_rows(static_sims, pomdp_sims) %>%
    left_join(meta) %>%  ## include scenario information (sigmas; etc)
    mutate(state = states[state], action = actions[action]) %>%
    select(time, state, rep, method, sigma_m, sigma_g, value)

@@

```{r S2, fig.width=8, fig.cap="Simulations as in the main text, Figure 1, shown across varying growth noise levels and including MSY strategy for comparison."}
sims <- read_csv(file.path(log_dir, "sims.csv"), col_types = "inicnnn")

@@

```{r S3, fig.cap="Economic value as in Fig 2 main text, shown across different levels of environmental noise, including MSY strategy."}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g %in% c("0.1", "0.15")) %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

@@

```{r overest, eval=!file.exists(file.path(log_dir, "pomdp_overest_sims.csv"))}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
write_csv(pomdp_overest_sims, file.path(log_dir, "pomdp_overest_sims.csv"))
```

@@

```{r}
pomdp_overest_sims <- read_csv(file.path(log_dir, "pomdp_overest_sims.csv")) %>% 
  mutate(scenario = as.character(scenario))

overest <-
bind_rows(static_sims, pomdp_overest_sims) %>%
  left_join(meta, by = "scenario") %>%  ## include scenario information (sigmas; etc)
  mutate(state = states[state], action = actions[action]) %>%
  select(time, state, rep, method, sigma_m, sigma_g, value) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  filter(sigma_g == "0.15") %>% 
  ungroup()

@@

```{r S4, fig.cap="over-estimating measurement uncertainty using POMDP, as in Fig 3 main text."}
read_csv(file.path(log_dir, "overest_sims.csv")) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))
```

@@

```{r S5, fig.cap="The CE policy is identical to the solution found by SDP under very small noise.  MSY and TAC can be seen to correspond to lower escapements at small stock sizes, since they continue to harvest stocks that are below $B_{MSY}$."}
bind_rows(policy_table,
  data_frame(state = states, 
             policy = "SDP",
             harvest = actions[mdp$policy],
             escapement = states - actions[mdp$policy])) %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8)) + 
  labs(caption = "SDP solution when sigma_g = 0.1")
```

@@

```{r S6, fig.cap="For large growth noise, the escapement under SDP is still constant but very slightly higher than the (deterministic) CE solution, $S>D$."}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0) %>%
  pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount)

@@

```{r}
p1 <- recode_policies %>%
  ggplot(aes(state, escapement, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.8)) +
  theme(legend.position = "none")

p2 <- recode_policies %>%
  ggplot(aes(state, harvest, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.6)) + 
  theme(legend.position = "bottom")

@@

```{r S7, fig.height=10, fig.width=5}
p3 <- read_csv(file.path(log_dir, "priors.csv")) %>%
ggplot(aes(state, prior, col = policy)) + 
  geom_line(lwd=1) +
  coord_cartesian(xlim = c(0,1)) + 
  theme(legend.position = "none")

gridExtra::grid.arrange(p1, p2, p3, ncol=1)
```

@@

```{r S8, fig.cap="Observation, True state, and Harvest quota over the course of a single simulation under POMDP management."}
sim$df %>%
  select(-value) %>%
  mutate(state = states[state], action = actions[action], obs = observations[obs]) %>%
  gather(variable, stock, -time) %>%
  ggplot(aes(time, stock, color = variable)) + 
  geom_line(lwd=1)  + scale_color_manual(values = unname(colors))
```

@@

```{r S9, fig.cap="The evolution of the POMDP prior belief distribution over the course of the simulation."}
sim$state_posterior %>% 
  data.frame(time = 1:Tmax) %>%
  filter(time %in% seq(1,Tmax, by = 3)) %>%
  gather(state, probability, -time, factor_key =TRUE) %>% 
  mutate(state = states[as.numeric(state)]) %>% 
  ggplot(aes(state, probability, group = time, alpha = time)) + 
  geom_line(lwd = 1) + 
  coord_cartesian(xlim = c(0,1.5))
